---
output:
  html_document:
    theme: united
---

```{r include=FALSE, echo=FALSE}
library(knitr)
opts_chunk$set(message=FALSE, warning=FALSE)
datasets <- shiny_data$datasets
name <- shiny_data$name
```

`r name` is a research tool for aggregating across studies in the language
acquisition literature. Currently, `r name` contains meta-analyses in `r nrow(datasets)` domains
of language acquisition, with `r sum(as.numeric(datasets$N), na.rm = TRUE)`
studies in total. These studies can be used to
obtain better estimates of effect sizes across different domains, methods, and ages.
Using our power calculator, researchers can use these estimates to plan appropriate
sample sizes for prospective studies. More generally, `r name` can be used as a
theoretical tool for exploring patterns in development across language acquisition
domains.

Individual meta-analyses:

```{r results='asis', echo=FALSE}
for (i in 1:nrow(datasets)) {
  dataset <- datasets[i,]
  cat(sprintf("  * __%s__ [%s](%s) [N = %s]\n\n    %s\n\n",
              dataset$name, dataset$citation, dataset$link, dataset$N, dataset$description))
}
```

Created by Molly Lewis, Mika Braginsky, Christina Bergmann, Sho Tsuji,
Alejandrina Cristia, and Michael C. Frank.

Contact: mll@stanford.edu
