---
title: "Within Subject Effect sizes"
author: "Molly Lewis"
date: "This report was rendered on `r Sys.Date()` and will be automatically re-rendered nightly, reflecting any changes in the data or code."
---

```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#ggplot2::theme_set(langcog::theme_mikabr(base_family = "Ubuntu"))
source("../dashboard/global.R", chdir = TRUE)

library(metafor)
library(tidyverse)
```

Exploring issue with differences in effect size as a function of how its calculated. Described in more detail [here](https://github.com/langcog/metalab/issues/113).

```{r, }
all_data = all_data %>%
            mutate(es_type = ifelse(es_method == "special_case", "special_case", 
                                 ifelse(es_method == "between", "between",
                                        ifelse(es_method %in% c("t_two", "f_two", "d_two",
                                                                "subj_diff_two"), "subj-level",
                                               "group-level"))))


es.counts = all_data %>%
  filter(dataset != "Pointing and vocabulary (longitudinal)") %>%
  select(dataset,es_method, participant_design, es_type) %>%
  group_by(dataset, es_method, es_type) %>%
  summarise(n = n(),
            participant_design = participant_design[1]) %>%
  arrange(es_method) 

ggplot(es.counts, aes(x = es_method, fill = es_type, group= es_type, y = n)) +
         geom_bar(stat= "identity", position = "dodge") +
  theme_bw() +
  ylab("n studies") +
  facet_wrap(~dataset, scales = "free_y") + 
  scale_x_discrete(drop=TRUE) +
  theme(axis.text.x  = element_text(angle=90, vjust = .5))
```

It looks like this issue is primary problematic for vowel discrimination and potentially IDS. For IDS ([Dunst, et al.](http://earlyliteracylearning.org/cellreviews/cellreviews_v5_n1.pdf)), we don't really know how d was calculated. 

For vowel discrimination, let's look at whether there's a difference in effect size as a funciton of how it was calculated.
```{r}
within.only.vowel.native = all_data %>%
  filter(dataset == "Vowel discrimination (native)") %>%
  filter(es_type != "special_case" & es_type != "between") 

ggplot(within.only.vowel.native, aes(x = es_type, y = d_calc)) +
  geom_boxplot()

table(within.only.vowel.native$es_type, within.only.vowel.native$method)
# within subject are central fixation and HPP

table(within.only.vowel.native$es_type, within.only.vowel.native$response_mode)
# all within subject are central fixation and HPP (method) OR eyetracing (response_mode)

rma(d_calc ~ mean_age + es_type + response_mode , vi = d_var_calc, data = within.only.vowel.native)

within.only.vowel.nnative = all_data %>%
  filter(dataset == "Vowel discrimination (non-native)") %>%
  filter(es_type != "special_case" & es_type != "between") 

ggplot(within.only.vowel.nnative, aes(x = es_type, y = d_calc)) +
  geom_boxplot()

table(within.only.vowel.nnative$es_type, within.only.vowel.nnative$method)
# within subject are central fixation and HPP

table(within.only.vowel.nnative$es_type, within.only.vowel.nnative$response_mode)
# all within subject are central fixation and HPP (method) OR eyetracing (response_mode)


rma(d_calc ~ mean_age + es_type , vi = d_var_calc, data = within.only.vowel.nnative)

```
In a simple anaylsis subj-level es claculations are overall lower than group-level. But subj-level calculations are perfectly correlated for native with es_type/method. So, hard to know what's going on here.

```{r, levels plot}
# need to recompute datasets summary data, based on filtered all_data
datasets <- datasets %>%
  rename(dataset = name) %>%
  select(-num_experiments, -num_papers, -num_subjects) %>%
  filter(dataset != "Statistical word segementation") %>% 
  filter(dataset != "Pointing and vocabulary (longitudinal)")

# rename pointing and vocabulary 
datasets$name = plyr::mapvalues(datasets$name, from = c("Pointing and vocabulary (concurrent)"), 
                                to = c("Pointing and vocabulary"))

all_data$dataset = plyr::mapvalues(all_data$dataset , from = c("Pointing and vocabulary (concurrent)"),
                                   to = c("Pointing and vocabulary"))

# make levels df
ld.df = data.frame(dataset = datasets$name,
                   domain = c("Prosody", "Words", "Communication", "Sounds",
                              "Sounds", "Sounds", "Sounds", "Sounds", "Words",
                              "Words", "Communication", "Words"))

ld.df$domain = factor(ld.df$domain, levels = c("Prosody","Sounds", "Words", "Communication"))

all_data_groups = all_data %>%
  filter(es_type != "subj-level" | es_method == "d_two") # include IDS because we don't know because based on d

single_method_datasets = all_data_groups %>%
  group_by(dataset) %>%
  summarise(n_methods = length(levels(as.factor(method)))) %>%
  filter(n_methods == 1) %>%
  .[["dataset"]]

# get model fits
all_data.resid = data.frame()
for (i in 1:length(datasets$name)) {
    d = filter(all_data_groups, dataset == datasets$name[i])
    if (datasets$name[i] %in% single_method_datasets) {
      full.model = rma(d_calc, vi = d_var_calc, data = d)
    } else {
      full.model = rma(d_calc ~ method, vi = d_var_calc, data = d)
    }
  
  d = as.data.frame(rstandard(full.model)$resid) %>%
       cbind(d) %>%
       rename(residual.d = `rstandard(full.model)$resid`) %>%
       mutate(residual.d = residual.d + full.model$b[1]) %>% # add in intercept term
       inner_join(all_data) 
  
  all_data.resid = rbind(all_data.resid,d)
}

# merge in levels
residualized.es = all_data.resid %>%
          left_join(ld.df) %>%
          filter(dataset != "Statistical sound category learning") %>%
          filter(dataset != "Phonotactic learning") %>%
          mutate(age.years = mean_age/365) %>%
          filter(age.years < 3)

fs = 16
ggplot(residualized.es, aes(x = age.years, y = residual.d, col = dataset)) +
  facet_grid(~ domain) +
  geom_point(aes(size = n), alpha = .1, data = filter(residualized.es, residual.d > -.5 & residual.d < 2.5 )) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_line(stat="smooth", method="lm", se = FALSE, size = 1, formula = y ~ log(x)) +
  coord_cartesian(ylim = c(-.5, 2.5), xlim = c(0, 3.1)) +  # doesn't remove data from geom_smooth
  xlab("Age (years)") +
  ylab("Method-residualized\n effect size") +
  theme_bw() +
  scale_color_solarized() +
  theme(legend.position = "none",
        legend.key = element_blank(),
        axis.line= element_line(size = 1),
        axis.text = element_text(colour = "black", size = fs),
        strip.text.x = element_text(size = 14),
        axis.title = element_text(colour = "black", size = fs),
        strip.background = element_rect(fill="grey"))
```
Even when exclding within-subject ES for vowel discrimination, meta-meta plot looks mostly the same.

