---
title: "Reproducability analyses"
author: "Molly Lewis and Christina Bergmann"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---
  
# Introduction


```{r}
rm(list=ls())
library(knitr)
library(metafor)
opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)

```

```{r}
setwd("../")
source('global.R')
source('multiplot.R')

```


# P-curve -- corrects for selective reporting on the basis of significance (fewer insignificant results)
```{r}
all_data$p_curve_stat = as.numeric(ifelse(!is.na(all_data$t), all_data$t, 
                               ifelse(!is.na(all_data$F), all_data$F, 'NA')))


                               
                               
                              


```



# Trim-and-fill -- corrects for selective reporting on the basis of effect size (fewer small effects; Duval & Tweedie, 2000a, 2000b)
```{r}
### fit random-effects model and plot
datasets = unique(all_data$dataset)

for (i in 1:length(datasets)) {
  my_data = all_data[all_data$dataset ==  datasets[i],]
  res <- rma(d, d_var, data = my_data)
  taf <- trimfill(res)
  funnel(taf, main = my_data$dataset[1])
}

res <- rma(d, d_var, data = all_data)
taf <- trimfill(res)
funnel(taf, main = "all data")
```

# Exclusions
# Publication Bias (years vs. effect sizes)
# Lab-based moderators (first author, last author, diversity)
# Data availability/reporting standards
# Meta-analytic power
# Indiviual meta-analysis power