---
title: Metalab Research Networks from WOS
author: Molly Lewis
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    highlight: tango
    toc_float: false
    theme: cerulean
    code_folding: hide
---

```{r, setup, include = FALSE}
rm(list=ls())

library(knitr)
library(tidyr)
library(langcog)
library(tidyverse)
library(stringr)
library(bibliometrix) 
library(ggnetwork)
library(intergraph)
library(igraph)
library(broom)

# load data
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, echo = TRUE,
                      warning = FALSE, message = FALSE, cache = FALSE)
```

***
***

[Metalab](http://metalab.stanford.edu/) is a dataset of effect sizes across 13 different phenomenon in language acquistion experimental research (n > 850 effect sizes). Here, I ask whether properties of the commmunity structure of a literature predictive of measures of bias in that literature.

Summary of key findings:
  
  * Co-authorship networks that are more modular have a larger fail-safe-ns.
  * Co-authorship networks that have greater betweeness have less heterogenity across the literature.
  * For article networks with links added when an author in the references appears in both articles (author coupling), articles with more modularity have greater fail-safe-ns. 

***
***

```{r, include = F}
# Parameters:
MIN_NUM_PAPERS <- 5 # per MA
ANALYSES <- c("collaboration","coupling", "co-citation", "co-occurrences") # Analysis-network pairs of interest
NETWORKS <- c("authors", "authors", "references","keywords")
```

# Web of Science Data
```{r, include = F}
#see get_primary_to_get_dois.R script
# Get Web of Science data for each paper in metalab dataset
wos <- read_csv("data/wos_bib1_6.csv")

### Number of papers with dois in web of science in each MA:
source("../../dashboard/global.R", chdir = TRUE) # all_data (MA data at ES level)

paper.data = all_data %>%
  select(short_name, study_ID, n_1, n_2) %>%
  inner_join(dois, by = "study_ID") %>%
  mutate(doi = tolower(doi)) %>%
  group_by(doi, short_name) %>%
  summarize(n = mean(c(n_1, n_2), na.rm = T)) %>%
  select(short_name, n) 

ns = paper.data %>%
  inner_join(wos, by = c("doi" = "DI")) %>%
  group_by(short_name) %>%
  summarize(n.papers = n()) 

# kable(ns)

paper.data = paper.data %>%
  left_join(ns) %>%
  filter(n.papers > MIN_NUM_PAPERS) 

n.mas = length(unique(paper.data$short_name))
```

We merge the metalab dataset with the web of science database based on dois. MAs with `r MIN_NUM_PAPERS` or fewer papers are excluded. This leaves us with `r n.mas` MAs. Note that we're losing papers here in two ways - those that don't have dois (e.g. conference papers, n = approx. 40) and those with dois that are not in web of science (n = approx. 50).


# Literature Networks

We examine four different network-types using the web of science data:

  * __Collaboration authors__: Nodes are authors and links are co-authorships
  * __Coupling authors__: Nodes are articles and links are added when at least one author in a cited source appears in the bibliographies of both articles.
  * __Co-citation references__: Nodes are articles are links are cases where both are cited in a third article.
  * __Co-occurences keywords__: Nodes are keywords and links are where the two keywords co-occur in the same article.

Then for each MA (n = `r n.mas`), we create a network of each of the four network-types. For each of those networks (N = `r n.mas * 4`), we quantify five properties of the network:

  * __Overall modularity (Q)__: Roughly, the degree to which the network has a community structure
  * __Number of groups in the network__ (n.groups)
  * __Closeness__: Measure of the degree to which a node is near all other nodes in the network
  * __Betweeness__: Measure of centrality of graph based on shortest paths (high betweenness -> high centrality),.
  * __Degree__: Mean number of edges of nodes in the network

Plotted below are the network metrics for each of the `r n.mas * 4` networks.
```{r.fig.width = 9}
# Define network function.
getGraph <- function (my.paper.data, 
                        this.analysis,
                        this.network,
                        type,
                        remove.multiple = FALSE,
                        noloops = FALSE) {
    # note: when remove.multiple = TRUE, clustering functions fails on some networks

    # get web of science data for domain
    this.wos = left_join(my.paper.data, wos, by = c("doi" = "DI")) %>%
             as.data.frame() # necessary for biblioNetwork
    
    sep = ifelse(this.analysis == "co-citation", ". ", 
                 ifelse(this.network == "authors", ";", "; ")) # bibliometrix_1_6

    # make the network
    this.net <- biblioNetwork(this.wos, 
                   analysis = this.analysis, 
                   network = this.network, 
                   sep = sep) 
    
    # get network into useable form
    if (length(this.net > 0)) {
      # munge the network
      graph <- graph.adjacency(this.net, mode = "undirected")
      graph <- igraph::simplify(graph, remove.multiple = remove.multiple, 
                                remove.loops = noloops)
      
      if (type == "plot"){
        
        gn = ggnetwork(asNetwork(graph)) # make into df for tidy plotting
          
      } else if (type == "stats"){
        
        clustering = cluster_leading_eigen(graph, options = list(maxiter = 1000000))
        closeness = mean(estimate_closeness(graph, cutoff = 100))
        betweeness = mean(estimate_betweenness(graph, cutoff = 100))
        degree = mean(igraph::degree(graph))
        
      }
    }
    
    # return stuff
      if (type == "plot"){ 
        
          cc <- try(gn, silent = TRUE)  # gets rid of too-small networks
          
          if(!is(cc,"try-error")) {
             return(gn)
          } 
          
      } else if (type == "stats") {
        
            data.frame(analysis = this.analysis,
                  network = this.network,
                  Q = round(clustering$modularity, 4), 
                  n.groups = round(length(clustering), 4),
                  closeness  = round(closeness, 4),
                  betweeness  = round(betweeness, 4),
                  degree = mean(degree))
      }
}
```


```{r}
# Make all networks and get network measures 
analyses_list <- rep(ANALYSES, each = n.mas) 
networks_list <- rep(NETWORKS, each = n.mas)

dfs <- paper.data %>% 
  mutate_each(funs(as.factor)) %>%
  split(.$short_name) %>%
  rep(length(ANALYSES))

args = list(dfs, analyses_list, networks_list)

modularity.data = args %>%
  pmap(getGraph, "stats") %>%
  bind_rows(.id = "short_name")

modularity.data.long = modularity.data %>%
    mutate(closeness = log(closeness),
            betweeness = log(betweeness),
            degree = log(degree)) %>%
    gather("network.measure", "network.value", 4:8) %>%
    unite(network, analysis, network, sep = ".")
```

```{r, figure.height = 12}
ggplot(modularity.data.long, aes(x = short_name, 
                                 y = network.value)) +
        geom_bar(stat = "identity", aes(fill = short_name))  +
        facet_wrap(network.measure ~ network, 
                   ncol = 4, scales = "free") +
        ggtitle("Network summary statistics") +
        theme_bw() +
        theme(axis.text.x = element_blank()) 
```

# Literature Bias
For each meta-analysis, we examine three aspects of the literature:

  * __Owin's fail-safe-n__: Number of studies that would need to be added in order to reduce the effect size to 0. Large numbers indicate more robust literatures.
  * __Effect size__: Meta-analytic estimate of effect size, controling for age.
  * __$tau^2$__: Estimate of the degree of heterogenity across studies in the literature.
    
Plotted below are the bias estimates for each of the literatures in our dataset.
```{r}
all_mas = read.csv("ES_data_for_networks2.csv") # overall ES data

ma.es = all_mas %>%
  select(short_name, overall.d.age,
         fsn_string,  tau2 ) %>% 
  mutate(overall.d.age = abs(overall.d.age),
         tau2 = log(tau2)) %>%
  rename(fail_safe_n = fsn_string) %>%
  gather("bias.measure", "bias.value", 2:4) 
```

```{r, fig.height = 2}
ma.es %>%
  filter(short_name %in% modularity.data.long$short_name) %>%
  ggplot(aes(x = short_name, y = bias.value)) +
        geom_bar(stat = "identity", aes(fill = short_name))  +
        facet_wrap(~bias.measure, scales = "free") +
        ggtitle("Bias summary statistics") +
        theme_bw() +
        theme(axis.text.x = element_blank()) 
```

# Correlations between network properties and bias
Given properties of the networks and estimates of the scientific bias in each literature, we ask whether these two measures are correlated. Specifically, we predict the bias value (e.g. fail-safe-n) with the network value (e.g. modularity), controlling for the number of papers in the MA, and weighting the MAs by the number of studies in the literature. We fit a seperate model for each bias-network pair, for each network type (e.g. co-citation references).
```{r}
net.es = left_join(modularity.data.long, ma.es) %>%
  dplyr::as_data_frame() %>%
  left_join(ns)

corr.sigs = net.es %>%
  filter(is.finite(network.value) & is.finite(bias.value)) %>%
  group_by(network, bias.measure, network.measure) %>%
  do(tidy(lm(bias.value ~ n.papers + network.value, weights = .$n.papers, data=.))) %>%
  filter(term == "network.value") %>%
  mutate(sig.col = ifelse(p.value < .05, "sig", "nsig")) %>%
  select(estimate, sig.col) %>%
  mutate(network.value = Inf, bias.value = Inf) # this is a hack
```

```{r}
# Define plotting functions
network_plot <- function(d, analysis, network){
  networkname <- paste(analysis, network, sep = ".")
  
  d %>%
    split(.$short_name) %>%
    map(getGraph, analysis, network, "plot") %>%
    bind_rows(.id = "short_name") %>%
    ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
       geom_edges(color = "grey50") +
       facet_wrap(~ short_name) +
       geom_nodes(aes(color = short_name)) +
       ggtitle(networkname) +
       theme_blank() +
       theme(legend.position = "none")
}

corr_plot <- function(d, corrs, analysis, network){
  networkname <- paste(analysis, network, sep = ".")
  
  ggplot(filter(d, network == networkname), 
       aes(x = network.value, y = bias.value)) +
     geom_rect(data = filter(corrs, network == networkname),
              aes(fill = sig.col), 
            xmin = -Inf, xmax = Inf,
            ymin = -Inf, ymax = Inf, alpha = 0.2) +
    geom_point(aes(size = n.papers, color = short_name)) +
    geom_smooth(method= "lm", color = "black") +
    ggtitle(networkname)+
    facet_grid(bias.measure ~ network.measure, scales = "free") +
    scale_fill_manual(values = c( "grey99", "red1")) +
    theme_bw() +
    theme(legend.position = "none")
}
```




## Collaboration authors{.tabset}

### Networks
```{r}
p <- 1
network_plot(paper.data, ANALYSES[p], NETWORKS[p])
```

### Models
```{r}
corr_plot(net.es, corr.sigs, ANALYSES[p], NETWORKS[p])
```

Each point corresponds to a meta-analysis (MA). Size of the point corresponds to number of papers in MA. Red facets indicate models where the network measure is a significant predictor of the bias value (controling for number of papers).


## Coupling authors{.tabset}

### Networks
```{r}
p <- 2
network_plot(paper.data, ANALYSES[p], NETWORKS[p])
```

### Models
```{r}
corr_plot(net.es, corr.sigs, ANALYSES[p], NETWORKS[p])
```

## Co-citation references{.tabset}

### Networks
```{r}
p <- 3
network_plot(paper.data, ANALYSES[p], NETWORKS[p])
```

### Models
```{r}
corr_plot(net.es, corr.sigs, ANALYSES[p], NETWORKS[p])
```

## Co-occurences keywords{.tabset}

### Networks
```{r}
p <- 4
network_plot(paper.data, ANALYSES[p], NETWORKS[p])
```

### Models
```{r}
corr_plot(net.es, corr.sigs, ANALYSES[p], NETWORKS[p])
```
