---
output:
  html_document
---

```{r include=FALSE, echo=FALSE}
library(shiny)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = FALSE)
datasets <- shiny_data$datasets
```

MetaLab is a research tool for aggregating across studies in the language 
acquisition literature. Currently, MetaLab contains
`r as.integer(sum(as.numeric(datasets$num_experiments), na.rm = TRUE))` effect sizes across
meta-analyses in `r nrow(datasets)` domains of language acquisition, based on
data from `r as.integer(sum(as.numeric(datasets$num_papers), na.rm = TRUE))` papers collecting
`r as.integer(sum(as.numeric(datasets$num_subjects), na.rm = TRUE))` subjects. These studies
can be used to obtain better estimates of effect sizes across different domains,
methods, and ages. Using our power calculator, researchers can use these
estimates to plan appropriate sample sizes for prospective studies. More
generally, MetaLab can be used as a theoretical tool for exploring patterns in
development across language acquisition domains.

Individual meta-analyses:

```{r results='asis', echo=FALSE}
for (i in 1:nrow(datasets)) {
  dataset <- datasets[i,]
  cat(sprintf("  * __%s__ [%s](%s) [N papers = %s, N effect sizes = %s]\n\n    %s\n\n",
              dataset$name, dataset$citation, dataset$link, dataset$num_papers, dataset$num_experiments, dataset$description))
}
```

Here are some `r a("instructional materials", target = "_blank", href = "https://docs.google.com/document/d/1rJDaBLTDpYcCeu0LH9E13qnC_ROarGyPXaRT-UBGBhE/edit")` on creating new meta-analyses.

Created by Molly Lewis, Mika Braginsky, Christina Bergmann, Sho Tsuji,
Alejandrina Cristia, and Michael C. Frank.

Contact: mll@stanford.edu
